Hydras \& Co.

### 2023-02-26 doc/hydras.tex
Implicits (#143)
* fix an inconsistent section numbering

* small correction in latex document

* small correction in latex document

* implicit arguments for impHn (to do: iffH, existH, andH, etc.)

* implicit arguments for notH (to do: iffH, existH, andH, etc.)

* implicit arguments for forallH (to do: iffH, existH, andH, etc.)

* implicit arguments for orH (to do: iffH, existH, andH, etc.)

* implicit arguments for andH (to do: iffH, existH, etc.)

* implicit arguments for iffH (to do:  existH, etc.)

* implicit arguments for equal (to do:  existH, etc.)

* implicit arguments for existH (to

\part{Ackermann, G\"{o}del, Peano\,\dots}
This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

Some changes are made to the aforementionned libraries, mainly because of the recent evolution of coq and its libraries. Nevertheless, the definitions, lemmas and theorems of the original contribution have been kept in this new release.

\emph{\color{red!80}This maintenance job has just started, and will probably be long to complete. Help is welcome!}

\include{chapter-primrec}
\include{chapter-fol}

>>>>

\part{Ackermann, G\"{o}del, Peano\,\dots}

\include{chap-intro-goedel}
\include{chapter-primrec} 
\include{chapter-fol}
